### 2015-02-03 paper_20_sdo.tex
more typos fixed

\subsection{THE SOFTWARE DEVELOPMENT LIFECYCLE}
    The discipline of software engineering has created a workflow for developing
    software.  
    This workflow is called the \textit{Software Development Life Cycle (SDLC)}.
    SDLC can be defined as \cite{Ruparelia2010}:
    \begin{quote}
     [...] a conceptual framework or process that considers the structure of the stages
     involved in the development of an application from its initial feasibility study
     through to its deployment in the field and maintenance.
    \end{quote}
    While the SDLC states what needs to be done, there are numerous models 
    that formalize exactly how to perform the SDLC.  The models contain
    steps that are commonly referred to as a phases. A few of the popular
    models are described below.

@@

        The spiral model for software development was presented by Boehm in 1986
        \cite{Boehm1986, Boehm1988}. 
        The goal of the spiral mode of software development is very risk-driven.
        A software project will start with many small and quick iterations. 
        Each iteration will cover the following 4 basic steps. 
        \begin{enumerate}
            \item Determine Objectives
            \item Identify Risks
            \item Develop and Test
            \item Plan Next Iteration
        \end{enumerate}
        This model allows software to be built over a series of iterations
        without risking too much time or effort in any single iteration.
        Sprial requires a very adaptive management approach
        as well as flexibility of the key stakeholders \cite{Ruparelia2010}.
        It can also be difficult to identify risks that will occur in future
        iterations.
        Figure \ref{fig:spiral} provides a bit more detail on the iterations
        and the overall process. 
        \begin{figure}[here]
            \centering
            \includegraphics[scale=.5]{images/spiral_model.png}
            \caption[SPIRAL SDLC MODEL]{Spiral SDLC Model \cite{Boehm2000} }
            \label{fig:spiral}
        \end{figure}

>>>>

\subsection{THE SOFTWARE DEVELOPMENT LIFE CYCLE}
    The discipline of software engineering has created a workflow for developing
    software.  
    This workflow is called the \textit{Software Development Life Cycle (SDLC)}.
    SDLC can be defined as \cite{Ruparelia2010}:
    \begin{quote}
     [...] a conceptual framework or process that considers the structure of the stages
     involved in the development of an application from its initial feasibility study
     through to its deployment in the field and maintenance.
    \end{quote}
    While the SDLC states what needs to be done, there are numerous models 
    that formalize exactly how to perform the SDLC.  The models contain
    steps that are commonly referred to as a phases. A few of the popular
    models are described below.

@@

        The spiral model for software development was presented by Boehm in 1986
        \cite{Boehm1986, Boehm1988}. 
        The goal of the spiral model of software development is very risk-driven.
        A software project will start with many small and quick iterations. 
        Each iteration will cover the following 4 basic steps. 
        \begin{enumerate}
            \item Determine Objectives
            \item Identify Risks
            \item Develop and Test
            \item Plan Next Iteration
        \end{enumerate}
        This model allows software to be built over a series of iterations
        without risking too much time or effort in any single iteration.
        Sprial requires a very adaptive management approach
        as well as flexibility of the key stakeholders \cite{Ruparelia2010}.
        It can also be difficult to identify risks that will occur in future
        iterations.
        Figure \ref{fig:spiral} provides a bit more detail on the iterations
        and the overall process. 
        \begin{figure}[here]
            \centering
            \includegraphics[scale=.5]{images/spiral_model.png}
            \caption[SPIRAL SDLC MODEL]{Spiral SDLC Model \cite{Boehm2000} }
            \label{fig:spiral}
        \end{figure}
